Galaxy Imaging with Generative Models: Insights from a Two-Models Framework

### 2025-03-14 MNRAS/galaxy-generative-models-overleaf-submit-2nd/article_MNRAS.tex
section 3.3.2 cont.

Figure~\ref{fig-UNet-denoising-train} presents the denoising results of two networks trained on datasets of different sizes, using an original image shared by both training sets. In contrast, Figure~\ref{fig-UNet-denoising-test} demonstrates the performance on an input image that was never included in the training data of either network, referred to as a \textit{validation image}. For both figures, the peak signal-to-noise ratio (PSNR) relative to the original image is provided above each image. The top row shows the input images (original or noisy) fed to the denoiser. The middle row displays the outputs from the \texttt{U-Net} trained with $N=100$ images, while the bottom row shows outputs from the \texttt{U-Net} trained with $N=100,000$ images. It is important to note that the networks were trained using noisy images without access to PSNR values or noise variance information.

>>>>

Figure~\ref{fig-UNet-denoising-train} presents the denoising results of two networks trained on datasets of different sizes, using an original image shared by both training sets. In contrast, Figure~\ref{fig-UNet-denoising-test} demonstrates the performance on an input image that was never included in the training data of either network, referred to as a \textit{validation image}. For both figures, the peak signal-to-noise ratio (PSNR) relative to the original image is provided above each image. {\color{red} This metric is appropriate, as it directly relates to the loss function used to optimize the denoiser. Additionally, in the context of score estimation, we focus on the overall denoising performance across the entire image, not just the galaxy pixels.} The top row shows the input images (original or noisy) fed to the denoiser. The middle row displays the outputs from the \texttt{U-Net} trained with $N=100$ images, while the bottom row shows outputs from the \texttt{U-Net} trained with $N=100,000$ images. It is important to note that the networks were trained using noisy images without access to PSNR values or noise variance information.
